Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-24 paper/current/main.tex
Added paragraph discussing predictions

>>>>

We also find that defining the gravity model as a function of embedding distance produces better predictions than does geographic distance.
Comparing predicted against actual flux, we find that using the embedding distance in the gravity function has lower error, and are closer than are predictions made using geographic distance (Fig.~\ref{fig:gravity_performance}c-d). 
Embedding distance also produces better predictions for pairs of organizations within the same country (Fig.~\ref{fig:supp:gravity_correlation}e-f) and for pairs of organizations in different countries (Fig.~\ref{fig:supp:gravity_correlation}g-h). 
We find that these predictions are robust whether we make predictions using a model fit on the subsets themselves (Fig.~\ref{fig:gravity_performance}e-h) or fit on the global data and then applied to the subsets (Fig. SI~\ref{fig:supp:gravity_prediction_subsets}). 
This performance is also much better than that using personalized page rank distance (Fig. SI~\ref{fig:supp:gravity_ppr}).
